Spatiotemporal Optimization of Cosmological Particel-Mesh Simulation

### 2023-01-11 docs/papers/sto/sto.tex
Draft: a few sentences on TO

We use a spline to model the function $a(t)$ that maps uniformly sampled $t$
values to optimally distributed $a$ time steps.
The spline is parameterized with a number of control points that are updated
during training.
The gradients (i.e. cotangents) are back propagated from an array of integration
time steps to the control points through a VJP transformation of $a(t)$.

>>>>

We use a spline to model the function $a(t)$ that maps uniformly sampled $t$
values to optimally distributed $a$ time steps.
The spline is parameterized with a number of control points that are optimized
during training.
The gradients (i.e. cotangents) are back propagated from the array of
integration time steps to the control points through a VJP transformation of
$a(t)$.

The time-dependence of the discrete symplectic integrator mainly enters through
the drift and kick factors in \eqref{DFK}.
Besides, the input features of the SO NNs could also depend on time.
Therefore when we perform TO together with SO, the force evaluation in
\eqref{DFK} which contains SO also becomes time-dependent and needs to be
optimized.
